\documentclass [PhD] {uclathes}



% \input {mymacros}                         % personal LaTeX macros
\usepackage{amsmath,amssymb}% for advanced math typesetting
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{oldlfont}
%\usepackage{natbib}
\usepackage{longtable}
\DeclareMathOperator{\sgn}{sgn}% Declare the sgn operator 
\DeclareMathOperator{\sign}{sign}% for those who insist on sign instead
\setcounter{tocdepth}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Usually things live in separate flies.
%
% \input {prelim}                           % preliminary page info

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                      %
%                          PRELIMINARY PAGES                           %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title          {Optimization of muon timing and searches for heavy
                long-lived charged particles with the
                Compact Muon Solenoid detector at the
                Large Hadron Collider}
\author         {Christopher Patrick Farrell}
\department     {Physics and Astronomy}
% Note:  degreeyear should be optional, but as of  5-Feb-96
% it seems required or you get a year of ``2''.   -johnh
\degreeyear     {2013}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chair          {Jay Hauser}
\member         {David Saltzberg}
\member         {Michael Gutperle}
\member         {Peter Felker}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\dedication     {\textsl{To my parents who have always been supportive of me}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\acknowledgments {
I want to say thank you to my advisor Jay Hauser whose teaching and advice allowed me to grow into a contributing member of the scientific community.
%for showing me how to investigate physics in a thorough and detailed manner.
Jay has always been available to aid in my understanding of problems and to give ideas when I was unsure of what to do going forward.
I could not have completed this work without him.

My development as a physicist has been shaped by discussions and guidance by my colleagues on CMS. 
The list includes but is not limited to 
Greg Rakness, Amanda Deisher, Mikhael Ignatenko, Chad Jarvis, Loic Quertenmont, and Todd Adams.

I am also grateful to David Saltzberg, Michael Gutperle, and Peter Felker for being willing to be on my committee and review my dissertation.

Finally I want to thank my family for their constant support. Especially, I want to thank my parents who have always worked to make my life as happy and fulfilling as possible.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vitaitem{1985}{Born, New Jersey, USA.}
\vitaitem{2008}{B.S.~Physics, University of Florida.}
\vitaitem{2008--present}{Research Assistant, University of California, Los Angeles.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\publication{
S.~Chatrchyan {\it et~al.} [CMS Collaboration],
``Search for heavy long-lived charged particles in $pp$ collisions at
  $\sqrt{s}=7$ TeV.''
{\em Phys.Lett.}, B713:408--433, 2012.
}

\publication{
The CMS Collaboration.
``Performance of CMS muon reconstruction in pp collision events at
  $\sqrt{s}=7$ TeV.''
{\em Journal of Instrumentation}, 7:2P, October 2012.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\rad}{rad}
\newcommand{\ias}{$I_{as}$}
\newcommand{\iasp}{$I_{as}^\prime$}
%\newcommand{\id}{$I_{d}$}                                                                                                                                                         
\newcommand{\ih}{$I_{h}$}
\newcommand{\dedx}{$dE/dx$}
\newcommand{\tof}{TOF}
\newcommand{\pt}{$p_{T}$}
\newcommand{\invbeta}{$\beta^{-1}$}
\newcommand{\invbetac}{$1/\beta, $}
\newcommand{\invbetap}{$1/\beta. $}
\newcommand{\tkonly}{{\em track only}}
\newcommand{\tktof}{{\em muon+track}}
\newcommand{\multi}{{\em multiple charge}}
\newcommand{\muononly}{{\em muon only}}
\newcommand{\fract}{{\em fractional charge}}

\newcommand{\stau}{$\tilde \tau _1 \ $}
\newcommand{\smu}{$\tilde \mu _1 \ $}
\newcommand{\sel}{$\tilde e _1 \ $}
\newcommand{\stp}{$\tilde t _1 \ $}
\newcommand{\gluino}{$\tilde g \ $}
\newcommand{\ETM}{$E_t^{miss} \ $}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\abstract       {
Proton--proton collisions at the Large Hadron Collider at $\sqrt{s} =$ 7 and 8 TeV are studied using the Compact Muon Solenoid (CMS) detector.
The measurement and improvements to the arrival time of particles to the muon system of CMS is detailed.
The timing is used to associate the particle with the correct proton--proton crossing and to classify the particle.
%One type of particle timing can help identify is new long-lived charged particles predicted in many theories of new physics, such as supersymmetry.
Additionally, four analyses are presented that use timing and ionization energy loss to search for the production of long-lived charged particles 
predicted in many theories of new physics. The searches are sensitive to a variety of signatures,
including the possibility that the particles will only be detectable during part of their passage through the CMS detector.
Limits are placed on the production of long-lived gluinos, stops, staus, and multiply charged particles.
The limits are the most stringent in the world to date.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin {document}
%\bibliographystyle{plain}
\makeintropages

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Ordinarily each chapter (at least) is in a separate file.
\input{introduction}

\input{theory}

\input{apparatus}

\input{timing}

\input{search}

\input{conclusion}

%\input{bibliography}

\newpage
\bibliographystyle{unsrt}
%\bibliographystyle{uclathes}
\bibliography{references}


\end {document}

